### 2022-12-02 ms.rmd
Added details in for back-transforming to Q10

# % change in acclimation
p_change_f <- ((f_acclim - f_acute) / f_acute); quantile(p_change_f, c(0.025, 0.975))
p_change_m <- ((m_acclim - m_acute) / m_acute); quantile(p_change_m, c(0.025, 0.975))
p_change_t <- ((t_acclim - t_acute) / t_acute); quantile(p_change_t, c(0.025, 0.975))

# But this is the % change on the log scale. We can also see what the Q10 change is..NEED TO BE CHECKED CAREFULLY
f_q10 <-exp((f_acclim - f_acute)-1); mean(f_q10); quantile(f_q10, c(0.025, 0.975))
m_q10 <-exp((m_acclim - m_acute)-1); mean(m_q10); quantile(m_q10, c(0.025, 0.975))
t_q10 <-exp((t_acclim - t_acute)-1); mean(t_q10); quantile(t_q10, c(0.025, 0.975))

@@

  p1.2
```

@@

orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = "lnRRQ10", angle = 45)

@@

   phylo
ggsave(filename = "fig1.png", path = "../output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
```

>>>>

# Q10 values for each category. Effect sizes are quite small really
   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10)
  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10)
   m_acute_Q10 <- exp(m_acute) ; mean(f_acute_Q10)
  m_acclim_Q10 <- exp(m_acclim); mean(f_acclim_Q10)
   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10)
  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10)

# % change in acclimation on log scale
  p_change_f <- ((f_acclim - f_acute) / f_acute); quantile(p_change_f, c(0.025, 0.975))
  p_change_m <- ((m_acclim - m_acute) / m_acute); quantile(p_change_m, c(0.025, 0.975))
  p_change_t <- ((t_acclim - t_acute) / t_acute); quantile(p_change_t, c(0.025, 0.975))

# % change on Q10 scale
  p_change_f_q10 <- exp(f_acclim - f_acute)-1; quantile(p_change_f_q10, c(0.025, 0.975))
  p_change_m_q10 <- exp(m_acclim - m_acute)-1; quantile(p_change_m_q10, c(0.025, 0.975))
  p_change_t_q10 <- exp(t_acclim - t_acute)-1; quantile(p_change_t_q10, c(0.025, 0.975))

@@

  p1.2
  ggsave(p1.2, filename = "./output/figures/fig1.png", )
```

@@

ptm <- orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS"))
ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

@@

   phylo
ggsave(filename = "fig3.png", path = "./output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
```
